### 2018-12-28 Sections/protocols_for_the_quantum_internet.tex
Formatting update

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{GHZ_LO_prep}
	\captionspacefig \caption{Linear optics circuit for the non-deterministic preparation of 3-qubit polarisation-encoded GHZ states \cite{ZeilingerPan}. A BBO SPDC source is pumped into the double excitation regime. Following evolution through the linear optics network, measurement of a photon in the tigger mode ($T$) heralds the preparation of a GHZ state across modes $D1$, $D2$ and $D3$.}\label{fig:GHZ_LO_prep}
\end{figure}

@@

Of particular interest to metrology\index{Quantum metrology} and CV quantum computing\index{Continuous-variables!Quantum computation} in particular, are squeezed states, states which have been longitudinally distorted in phase-space. In the metrological context, squeezed states enable sub-shotnoise limited metrology \cite{???}, thereby outperforming any classical protocol, using, for example, coherent states.

@@

The most common form of photo-detection is using avalanche photo-diodes (APDs), which are cheap but non-number-resolving. Here a single photon excites an electron into the conduction band at a semiconductor junction, enabling a detectable current flow. However, a single excitation triggers an `avalanche' of further excitation making the magnitude of the detected current essentially unrelated to exact photon number.

@@

Furthermore, photo-detectors are subject to `dead-time'\index{Dead-time}, which renders them inactive for a finite recovery period following a detection event. This is of especial importance in time-bin-encoded schemes (Sec.~\ref{sec:time_bin}), where detectors must resolve photons over very short timescales on the order of nanoseconds. Dead-time can be modelled as a time-dependent efficiency of the form,
\begin{align}
\eta(t) = \left\{\begin{array}{cc}
 0, & t<\tau_\mathrm{dt} \\
 \eta_\mathrm{ss}, & t\geq\tau_\mathrm{dt} \\
\end{array}\right.,
\end{align}
where $t$ is time, $\tau_\mathrm{dt}$ is the detector's deadtime, and $\eta_\mathrm{ss}$ is the detector's steady-state efficiency (i.e when not dead).

@@

Mathematically, we are interested in the probability \mbox{$P(n_\mathrm{meas}=n_\mathrm{inc})$} that the measured number of photons ($n_\mathrm{meas}$) matches the actual number of incident photons ($n_\mathrm{inc}$). The structure of this expression will vary enormously depending on the details of the architecture (e.g multi-port interferometer vs fibre-loop). However, \cite{rohdeHuntington} presented a very general mathematical formalism applicable to all architectural variants. The simplest case to consider is the multi-port interferometer, owing to its perfect symmetry. The probability is simply the probability that no output mode from the multi-port contain multiple photons. A quick calculation yields,
\begin{align}
	P(n_\mathrm{meas}=n_\mathrm{inc}) = \frac{\eta^n m!}{m^n(m-n)!},
\end{align}
for efficiency $\eta$, not accounting for other lesser errors such as dark-counts. This is shown in Fig.~\ref{fig:multiplexed_pd}. For perfect efficiency, \mbox{$\eta=1$}, this probability always approaches unity in the limit of a large number of modes,
\begin{align}
\lim_{m\to\infty}P(n_\mathrm{meas}=n_\mathrm{inc})=1.
\end{align}

@@

%
% Homodyning
%

\subsection{Homodyning} \label{sec:homodyne} \index{Homodyne detection}

A homodyne detector interferes a state with a coherent state on a beamsplitter, which acts as a phase-reference\index{Phase!Reference}, before photo-detecting both output modes and taking the difference in the photon count-rates (Fig.~\ref{fig:homodyne}).

@@

Note that there is a break-even point, above which the protocol strictly increases fidelity, and below which strictly decreases it. This occurs at \mbox{$F_\mathrm{in}=1/2$}. Provided pairs can be communicated above this fidelity threshold, bootstrapped application of the protocol could be employed to boost entanglement fidelity asymptotically close to unity (but with exponential resource overhead, since each operation non-deterministically consumes two pairs to produce one). But below this threshold it is impossible to recover any more entanglement than we started with. This provides an example of an application where the protocol being implemented dictates strict requirements on network cost metrics. Specifically, assuming perfect Bell pairs to begin with, the routes by which they are communicated must strictly ensure entanglement fidelities of at least \mbox{$F=1/2$} upon reaching their destination. Here a type of \textsc{All or Nothing} networking strategy would be applicable -- if the fidelity requirement is not met, the state cannot be purified and might as well be thrown away to make way for other traffic.

@@

Often the light that arrives will be formed by a mixture of photons from different sources that emit incoherently, and different locations give rise to different phase-shifts $\phi$, resulting in a density matrix of the form,
\begin{align}
\hat\rho = \frac{1}{2} \left(\begin{matrix}{}
  0 & 0 & 0 & 0 \\
  0 & 1 & \mathcal{V}^* & 0 \\
  0 & \mathcal{V} & 1 & 0 \\
  0 & 0 & 0 & 0
\end{matrix}\right),
\end{align}
where $\mathcal{V}$ is the visibility, reflecting decoherence.

>>>>

\begin{figure}[!htbp]
	\includegraphics[clip=true, width=0.475\textwidth]{GHZ_LO_prep}
	\captionspacefig \caption{Linear optics circuit for the non-deterministic preparation of 3-qubit polarisation-encoded GHZ states \cite{bib:ZeilingerPan}. A BBO SPDC source is pumped into the double excitation regime. Following evolution through the linear optics network, measurement of a photon in the tigger mode ($T$) heralds the preparation of a GHZ state across modes $D1$, $D2$ and $D3$.}\label{fig:GHZ_LO_prep}
\end{figure}

@@

Of particular interest to metrology\index{Quantum metrology} and CV quantum computing\index{Continuous-variables!Quantum computation} in particular, are squeezed states, states which have been longitudinally distorted in phase-space. In the metrological context, squeezed states enable sub-shot-noise\index{Shot noise} limited metrology \cite{???}, thereby outperforming any classical protocol, using, for example, coherent states.

@@

The most common form of photo-detection is using avalanche photo-diodes (APDs), which are cheap but non-number-resolving. Here, a single photon excites an electron into the conduction band at a semiconductor junction, enabling a detectable current flow. However, a single excitation triggers an `avalanche' of further excitation making the magnitude of the detected current essentially unrelated to exact photon number.

@@

Furthermore, photo-detectors are subject to `dead-time'\index{Dead-time}, which renders them inactive for a finite recovery period following a detection event. This is of especial importance in time-bin-encoded schemes (Sec.~\ref{sec:time_bin}), where detectors must resolve photons over very short timescales on the order of nanoseconds. Dead-time can be modelled as a time-dependent efficiency of the form,
\begin{align}
\eta(t) = \left\{\begin{array}{cc}
 0, & t<\tau_\mathrm{dt} \\
 \eta_\mathrm{ss}, & t\geq\tau_\mathrm{dt} \\
\end{array}\right.,
\end{align}
where $t$ is time, $\tau_\mathrm{dt}$ is the detector's dead time\index{Dead time}, and $\eta_\mathrm{ss}$ is the detector's steady-state efficiency (i.e when not dead).

@@

Mathematically, we are interested in the probability \mbox{$P(n_\mathrm{meas}=n_\mathrm{inc})$} that the measured number of photons ($n_\mathrm{meas}$) matches the actual number of incident photons ($n_\mathrm{inc}$). The structure of this expression will vary enormously depending on the details of the architecture (e.g multi-port interferometer vs fibre-loop). However, \cite{bib:rohdeHuntington} presented a very general mathematical formalism applicable to all architectural variants. The simplest case to consider is the multi-port interferometer, owing to its perfect symmetry. The probability is simply the probability that no output mode from the multi-port contain multiple photons. A quick calculation yields,
\begin{align}
	P(n_\mathrm{meas}=n_\mathrm{inc}) = \frac{\eta^n m!}{m^n(m-n)!},
\end{align}
for efficiency $\eta$, not accounting for other lesser errors such as dark-counts. This is shown in Fig.~\ref{fig:multiplexed_pd}. For perfect efficiency, \mbox{$\eta=1$}, this probability always approaches unity in the limit of a large number of modes,
\begin{align}
\lim_{m\to\infty}P(n_\mathrm{meas}=n_\mathrm{inc})=1.
\end{align}

@@

%
% Homodyne detection
%

\subsection{Homodyne detection} \label{sec:homodyne} \index{Homodyne detection}

A homodyne detector interferes a state with a coherent state on a beamsplitter, which acts as a phase-reference\index{Phase!Reference}, before photo-detecting both output modes and taking the difference in the photon count-rates (Fig.~\ref{fig:homodyne}). This effectively allows us to observe `beating'\index{Beating} effects between the signal and reference probe.

@@

Note that there is a break-even point, above which the protocol strictly increases fidelity, and below which strictly decreases it. This occurs at \mbox{$F_\mathrm{in}=1/2$}. Provided pairs can be communicated above this fidelity threshold, bootstrapped application of the protocol could be employed to boost entanglement fidelity asymptotically close to unity (but with exponential resource overhead, since each operation non-deterministically consumes two pairs to produce one). But below this threshold it is impossible to recover any more entanglement than we started with. This provides an example of an application where the protocol being implemented dictates strict requirements on network cost metrics. Specifically, assuming perfect Bell pairs to begin with, the routes by which they are communicated must strictly ensure entanglement fidelities of at least \mbox{$F=1/2$} upon reaching their destination. Here, a type of \textsc{All or Nothing} networking strategy would be applicable -- if the fidelity requirement is not met, the state cannot be purified and might as well be thrown away to make way for other traffic.

@@

Often the light that arrives will be formed by a mixture of photons from different sources that emit incoherently, and different locations give rise to different phase-shifts $\phi$, resulting in a density matrix of the form,
\begin{align}
\hat\rho = \frac{1}{2} \begin{pmatrix}
  0 & 0 & 0 & 0 \\
  0 & 1 & \mathcal{V}^* & 0 \\
  0 & \mathcal{V} & 1 & 0 \\
  0 & 0 & 0 & 0
\end{pmatrix},
\end{align}
where $\mathcal{V}$ is the visibility, reflecting decoherence.

### 2018-12-28 Sections/quality_of_service.tex
Finito first round of indexing
Improved QM intro
Formatting update

This is the simplest construction of a code which protects against a single depolarising event. But it is not the most efficient, and numerous more resource-savvy codes for protecting against Pauli errors exist, such as Steane's 7-qubit code\index{Steane code} \cite{SteaneCode}.

@@

\subsection{Unitary error averaging} \index{Quantum error correction (QEC)}\index{Unitary error averaging}\label{sec:error_averaging}

Aside from the \textit{active} QoS techniques discussed until now, there is also a recently described \textit{passive} technique that requires no feedforward to operate. This technique, called \textit{unitary error averaging} \cite{MarshmanLundRohde}, is formulated specifically in the linear optical context. It is an open question whether it generalises to other models, such as conventional quantum circuits.

@@

\cite{MarshmanLundRohdeRalph} showed that by using an optical fanout\index{Fanout} operation, which splits a set of optical modes equally across multiple sets of modes in a type of redundant encoding\footnote{The optical fanout operation effectively maps single-photon states to W-states (Sec.~\ref{sec:W_state_prep})\index{W-states}.}, and passing each set through an independently manufactured copy of the imperfect unitary, $\tilde{U}_i$, upon performing a fan-in to recombine the modes, and post-selection on detecting all photons in the desired output modes, the output state will behave as if it had evolved through a network given by the arithmetic average of each of the imperfect copies of $\hat{U}_\mathrm{target}$,
\begin{align}
\hat{U}_\mathrm{av} = \frac{1}{M}\sum_{i=1}^M \tilde{U}_i.	
\end{align}
A schematic for the optical circuit is shown in Fig.~\ref{fig:error_av_circuit}.

@@

In \cite{RohdeHaselgrove} a derivation of a generalisation of the quantum Hamming bound\index{Quantum Hamming bound} for non-degenerate\footnote{In a non-degenerate code, all correctable errors map the codeword to orthogonal states. For degenerate codes\index{Degenerate codes} multiple distinct errors can map the codeword to the same state. The Hamming bound exploits the non-degeneracy using a counting or `pigeonholing' argument to count correctable errors.} QEC codes\index{Non-degenerate codes} was presented, where the number of located and unlocated errors were treated as independent parameters. They found that for non-degenerate codes the Hamming bound allows exactly twice as many located as unlocated errors. Specifically, for $t_l$ located errors and $t_u$ unlocated errors in an $n$-qubit non-degenerate code encoding $k$ logical qubits, QEC is possible provided that the number of errors satisfied,
\begin{align}
\sum_{i=0}^{t_u + \lfloor t_l/2 \rfloor} \binom{n}{i}3^i 2^k \leq 2^n.
\end{align}

@@

A single-qubit $Z$-rotation of angle $\theta$ on the Bloch sphere\index{Bloch sphere} is given by,
\begin{align}
	\hat{Z}(\theta) = e^{i\frac{\theta}{2}\hat{Z}} = \left(\begin{matrix}
  e^{i\frac{\theta}{2}} & 0 \\
  0 & e^{-i\frac{\theta}{2}}
\end{matrix}\right).
\end{align}
where $\hat{Z}$ is the usual Pauli phase-flip operator\index{Pauli!Operators} (Sec.~\ref{sec:circuit_model}). This operates on the physical basis states as,
\begin{align}
	\hat{Z}(\theta) \ket{0} &\to e^{i\frac{\theta}{2}}\ket{0}, \nonumber \\
	\hat{Z}(\theta) \ket{1} &\to e^{-i\frac{\theta}{2}}\ket{1}.
\end{align}

@@

Let us illustrate how this can be achieved using a simple example, whereby a single-qubit system couples with an environment which introduces a slow, unknown phase evolution. Discretising time, we can write this phase evolution as a Pauli $Z$-rotation on the Bloch sphere\index{Bloch sphere},
\begin{align}
	\hat{Z}(\theta) = e^{i\frac{\theta}{2}\hat{Z}} = \left(\begin{matrix}
  e^{i\frac{\theta}{2}} & 0 \\
  0 & e^{-i\frac{\theta}{2}}
\end{matrix}\right),
\end{align}
for some unknown, but small $\theta$. Next we observe that, quite obviously, a $Z$-rotation of angle $\theta$ can be trivially undone by applying another $Z$-rotation of angle $-\theta$, since,
\begin{align}
\hat{Z}(-\theta)\hat{Z}(\theta) = \hat{\mathbb{I}}.	
\end{align}

@@

Now if we proceed for two time-steps, once bit-flipped and another not, we have,
\begin{align}
\underbrace{\hat{Z}(\theta)}_{\mathrm{forward}}\cdot\underbrace{[\hat{X}\hat{Z}(\theta)\hat{X}]}_{\mathrm{reverse}} = \hat{\mathbb{I}},
\end{align}
and the unknown phase-rotation has been eliminated. The sequence is illustrated on the Bloch sphere\index{Bloch sphere} in Fig.~\ref{fig:bloch_sphere_dyn_dec}.

>>>>

This is the simplest construction of a code which protects against a single depolarising event. But it is not the most efficient, and numerous more resource-savvy codes for protecting against Pauli errors exist, such as Steane's 7-qubit code\index{Steane code} \cite{bib:SteaneCode}.

@@

\subsection{Unitary error averaging} \index{Quantum error correction (QEC)}\index{Unitary!Error averaging}\label{sec:error_averaging}

Aside from the \textit{active} QoS techniques discussed until now, there is also a recently described \textit{passive} technique that requires no feedforward to operate. This technique, called \textit{unitary error averaging} \cite{bib:MarshmanLundRohde}, is formulated specifically in the linear optical context. It is an open question whether it generalises to other models, such as conventional quantum circuits.

@@

\cite{bib:MarshmanLundRohdeRalph} showed that by using an optical fanout\index{Fanout} operation, which splits a set of optical modes equally across multiple sets of modes in a type of redundant encoding\footnote{The optical fanout operation effectively maps single-photon states to W-states (Sec.~\ref{sec:W_state_prep})\index{W-states}.}, and passing each set through an independently manufactured copy of the imperfect unitary, $\tilde{U}_i$, upon performing a fan-in to recombine the modes, and post-selection on detecting all photons in the desired output modes, the output state will behave as if it had evolved through a network given by the arithmetic average of each of the imperfect copies of $\hat{U}_\mathrm{target}$,
\begin{align}
\hat{U}_\mathrm{av} = \frac{1}{M}\sum_{i=1}^M \tilde{U}_i.	
\end{align}
A schematic for the optical circuit is shown in Fig.~\ref{fig:error_av_circuit}.

@@

In \cite{bib:RohdeHaselgrove} a derivation of a generalisation of the quantum Hamming bound\index{Quantum Hamming bound} for non-degenerate\footnote{In a non-degenerate code, all correctable errors map the codeword to orthogonal states. For degenerate codes\index{Degenerate codes} multiple distinct errors can map the codeword to the same state. The Hamming bound exploits the non-degeneracy using a counting or `pigeonholing' argument to count correctable errors.} QEC codes\index{Non-degenerate codes} was presented, where the number of located and unlocated errors were treated as independent parameters. They found that for non-degenerate codes the Hamming bound allows exactly twice as many located as unlocated errors. Specifically, for $t_l$ located errors and $t_u$ unlocated errors in an $n$-qubit non-degenerate code encoding $k$ logical qubits, QEC is possible provided that the number of errors satisfied,
\begin{align}
\sum_{i=0}^{t_u + \lfloor t_l/2 \rfloor} \binom{n}{i}3^i 2^k \leq 2^n.
\end{align}

@@

A single-qubit $Z$-rotation of angle $\theta$ on the Bloch sphere\index{Bloch sphere} is given by,
\begin{align}
	\hat{Z}(\theta) = e^{i\frac{\theta}{2}\hat{Z}} = \begin{pmatrix}
  e^{i\frac{\theta}{2}} & 0 \\
  0 & e^{-i\frac{\theta}{2}}
\end{pmatrix}.
\end{align}
where $\hat{Z}$ is the usual Pauli phase-flip operator\index{Pauli!Operators} (Sec.~\ref{sec:circuit_model}). This operates on the physical basis states as,
\begin{align}
	\hat{Z}(\theta) \ket{0} &\to e^{i\frac{\theta}{2}}\ket{0}, \nonumber \\
	\hat{Z}(\theta) \ket{1} &\to e^{-i\frac{\theta}{2}}\ket{1}.
\end{align}

@@

Let us illustrate how this can be achieved using a simple example, whereby a single-qubit system couples with an environment which introduces a slow, unknown phase evolution. Discretising time, we can write this phase evolution as a Pauli $Z$-rotation on the Bloch sphere\index{Bloch sphere},
\begin{align}
	\hat{Z}(\theta) = e^{i\frac{\theta}{2}\hat{Z}} = \begin{pmatrix}
  e^{i\frac{\theta}{2}} & 0 \\
  0 & e^{-i\frac{\theta}{2}}
\end{pmatrix},
\end{align}
for some unknown, but small $\theta$. Next we observe that, quite obviously, a $Z$-rotation of angle $\theta$ can be trivially undone by applying another $Z$-rotation of angle $-\theta$, since,
\begin{align}
\hat{Z}(-\theta)\hat{Z}(\theta) = \hat\openone.	
\end{align}

@@

Now if we proceed for two time-steps, once bit-flipped and another not, we have,
\begin{align}
\underbrace{\hat{Z}(\theta)}_{\mathrm{forward}}\cdot\underbrace{[\hat{X}\hat{Z}(\theta)\hat{X}]}_{\mathrm{reverse}} = \hat\openone,
\end{align}
and the unknown phase-rotation has been eliminated. The sequence is illustrated on the Bloch sphere\index{Bloch sphere} in Fig.~\ref{fig:bloch_sphere_dyn_dec}.
